Deep Reinforcement Learning for Conservation Decisions

### 2021-05-15 manuscript/manuscript.Rmd
Adding bits to convey practicality

## Training and tuning an agent
<!-- Maybe rename this as Training and Tuning an Agent -> how to practically get an agent up and running -->
<!-- Ecologist job to build environment; CS job to build agent 
      Ok so talk about this in very general terms
      selecting an agent, why you might want to use different ones
-->
Training a deep, model-free agent on an environment involves allowing the agent to interact with the environment for thousands or even millions of time steps.
The training period involves a trial and error process whereby the agent will perform an action and then receive feedback from the environment in the form of a reward. 
This process will repeat until the environment transitions to a terminal state, after which the environment will reset to some starting condition.
According to the algorithm that the agent follows, the agent will explore different state-action trajectories and use its experience to improve its policy.
The amount of time needed for an agent to learn high reward yielding behavior cannot be predetermined and depends on a host of factors including the amount of dedicated compute, the simulation complexity of the environment, model complexity of the agent and more.
Yet, overall, it has been well established that deep, model-free RL agents tend to be very sample inefficient [@cite], so it is recommended to provide a generous training budget for these agents.

>>>>

## Training and tuning an agent

Training a deep, model-free agent on an environment involves allowing the agent to interact with the environment for thousands or even millions of time steps.
The training period involves a trial and error process whereby the agent will perform an action and then receive feedback from the environment in the form of a reward. 
This process will repeat until the environment transitions to a terminal state, after which the environment will reset to some starting condition.
According to the algorithm that the agent follows, the agent will explore the state-action space and use its experience to improve its policy.
The amount of time needed for an agent to learn high reward yielding behavior cannot be predetermined and depends on a host of factors including the amount of dedicated compute, the simulation complexity of the environment, model complexity of the agent and more.
Yet, overall, it has been well established that deep, model-free RL agents tend to be very sample inefficient [@cite], so it is recommended to provide a generous training budget for these agents.
As practitioners, an advantage of using deep, model-free algorithms is that since they function autonomously and do not require any knowledge about the environment, we can readily test how these algorithms perform without knowing much about the environment's transition dynamics or all the inner workings of the algorithm.
